Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-18 paper.tex
{Dynamics of Anth... -> The Dynamics of ...}
Moved the Factors of anthropo to end of section 2
Minor sections/subsections fixing
refinements sections 1 and 2

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time (during the process of
\emph{adopting} a robot, for instance): we propose to go beyond the traditional
perception of anthropomorphism in robotics as a static feature that once
observed during a short-term interaction reflects a sustaining social effect.
Based on an extensive literature review previously
published~\cite{fink_anthropomorphism_2012} and field
experiments~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
not always the same but evolve over time, along with growing interaction and
experience with the robot, similar to how relationships among people evolve
over time \fixme{(cite Hinde, 1988)}. In fact, \cite{kanda_interactive_2004}
also hypothesized that people's attitude toward technological artifacts and
their relationship with them would evolve over time, and they were among the
first who described \emph{novelty effects} during a long-term study with an
interactive robot in a school.

\subsection{Measuring anthropomorphism}

Measuring anthropomorphism is challenging because the phenomenon is partialy
unconscious, its mediation is largely subject-dependent, and we found the
phenomenon generally difficult to verbalize for users.

To reduce subjectivity and still accurately account for psychological effects,
it appears necessary to interleave quantitative and qualitative assessments of
anthropomorphic effects.

We present in this section the methodology and techniques we have relied on to
assess anthropomorphic projections in two unrelated studies, the Roomba
experiment~\cite{fink_living_2013}, and the Dominos experiment.

\paragraph{Quantitative assessment of anthropomorphism} Quantitative data are
acquired by systematic annotations of human- robot interactions on video records
of the experiments. Six classes of interactions were identified as reflecting
active commitment of the users in the interaction (gestures, touches, talk to
the robot, show something to the robot, misbehave, look at the experimenter
because worried by the robot's behavior)

\paragraph{Qualitative assessment of anthropomorphism} The main tools for
qualitative measurement of anthropomorphic effect are questionnaires. We have
explored both Likert-scale and open questions.

\subsubsection{The Roomba experiment}

\begin{tikzpicture}[scale=0.5, y = 2cm]
%axis
\draw (0,0) -- coordinate (x axis mid) (20,0);
\draw (0,0) -- coordinate (y axis mid) (0,7);
%ticks
\foreach \x in {0,4,...,20}
    \draw (\x,1pt) -- (\x,-3pt);
\foreach \y in {1,...,7} 
    \draw[black!20] (20,\y) -- (-3pt,\y);
\foreach \y in {1,...,7} 
    \draw (-3pt, \y) node[anchor=east] {\y}; 
%labels
\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
\node at (2, -0.4) {\tiny expectations};
\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};

\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};

\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};

\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};

\caption{User perception of the Roomba robot over a 6 month period
($\sigma=15$).}

\label{roomba-perception}
\end{figure*}

\subsubsection{The Ranger experiment}

Questionnaires are analyzed such as points are 
attributed for key answers, leading to a 
qualitative score:

\begin{itemize}
    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
        hungry, tired}
    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
        always obey, could do a b\^{e}tise...}
    \item View robot as friend (1 point)
    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
        able to hear}
    \item Belief robot has feelings (2 points)
    \item Give anthropomorphic reasons for
        \begin{itemize}
            \item not leaving robot alone (1--3 points) {\it Would be sad when
                left alone}
            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn’t
                like to play any longer}
        \end{itemize}
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
    \caption{Quantitative assessment: here, six interactions modalities have
        been selected: showing something to the robot ({\tt show}), talking to
        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
        for exterior help by looking at the experimenter ({\tt look}). In each
        of the 14 experimental runs, we annotate and count the number of
        occurences of each of these interactions.  Highlighted runs 2.3, 2.4,
        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
        of interactions everytime the robot's behaviour changes from expected to
        unexpected or from unexpected to expected.}

    \label{interactions-per-run}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{ranger-interactions-vs-qualitative-score}
    \caption{We found a significant negative correlation ($p=0.048$) between the
    number of interactions and the qualitative anthropomorphic projections
    ($\sigma=13$).}
    \label{qualitative-score}
\end{figure}

\subsection{A Model of the Dynamics of Anthropomorphism}
\label{sec:dynamics-model}

>>>>

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time (during the process of
\emph{adopting} a robot, for instance): we propose to go beyond the traditional
perception of anthropomorphism in robotics as a static feature that once
observed during a short-term interaction reflects a sustaining social effect.
Based on an extensive literature review previously
published~\cite{fink_anthropomorphism_2012} and field
experiements~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
not always the same but evolve over time, along with growing interaction and
experience with the robot, similar to how relationships among people evolve
over time \fixme{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.}
\cite{kanda_interactive_2004} also hypothesized that people's attitude toward
technological artifacts and their relationship with them would evolve over
time, and they were among the first who described \textit{novelty effects}
during a long-term study with an interactive robot in a school.
